Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-07-18 longSC.tex
fix vn
You's comment

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. We use the notation $v_n$ instead of $v_{2}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
%While these product are reconstructed and normalized directly for NSC calculations,
The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

@@

\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
\label{sec:theory_allorder}
Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. 
We compare to event-by-event EKRT+viscous hydrodynamics predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.

>>>>

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
%While these product are reconstructed and normalized directly for NSC calculations,
The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

@@

\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
\label{sec:theory_allorder}
Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. 
We compare to event-by-event EKRT+viscous hydrodynamic predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.
